Carp\'{e} Data: Supporting Serendipitous Data Integration in Personal Information Management

### 2012-09-17 chi2012.tex
edits and changes

\subsection{Strategies: Successive Elimination vs Tallying}
As described in Discussion later, we noticed several different strategies that people used to evalutate each candidate selection. One common strategy was \emph{successive elimination} - to look at a single dimension at a time, starting with the most important, ruling out candidates that did not meet the required minimum for that value.  However, when there is no clear ``most important'' aspect, this  ``greedy-style'' can result in suboptimal decisions.  By comparison, a different strategy, which we called \emph{tallying the pros and cons}, kept all candidates around, and counted up the advantages and disadvantages of each, potentially weighing each factor by its perceived importance.  This strategy is less vulnerable to getting stuck in local maxima than the former.

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=8.5cm]{img/results}
\caption{The chosen restaurant/university for each participant, showing the choice on the x axis and frequency on the y axis under conditions A (blue) and B (red).}
\label{fig:results}
\end{center}
\end{figure}

@@

%+ ÊWhat did people think about it? 
% Ê Ê Ê ÊUsefulness,Ease,Confusion,etc

>>>>

\subsubsection{Candidate selection}

\begin{figure}[htb]
\begin{center}
\includegraphics[width=8.5cm]{img/results}
\caption{The chosen restaurant/university for each participant, showing the choice on the x axis and frequency on the y axis under conditions A (blue) and B (red).}
\label{fig:chosen_results}
\end{center}
\end{figure}

Since the tasks were subjective-choice, we could not evaluate the 'correctness' of people's answers.  However, to determine whether there was a difference in variability of answers between interface conditions, we histogrammed responses for each task and dataset for both conditions, visible in  Figure \ref{fig:chosen_results}. 
\subsection{Strategies: Successive Elimination vs Tallying}
As described in Discussion later, we noticed several different strategies that people used to evalutate each candidate selection. One common strategy was \emph{successive elimination} - to look at a single dimension at a time, starting with the most important, ruling out candidates that did not meet the required minimum for that value.  However, when there is no clear ``most important'' aspect, this  ``greedy-style'' can result in suboptimal decisions.  By comparison, a different strategy, which we called \emph{tallying the pros and cons}, kept all candidates around, and counted up the advantages and disadvantages of each, potentially weighing each factor by its perceived importance.  This strategy is less vulnerable to getting stuck in local maxima than the former.

@@

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=8.5cm]{img/survey}
\caption{The chosen restaurant/university for each participant, showing the choice on the x axis and frequency on the y axis under conditions A (blue) and B (red).}
\label{fig:survey}
\end{center}
\end{figure}

%+What did people think about it? 
% Usefulness,Ease,Confusion,etc
